### 2008-09-02 doc/client/client_technical.tex
added text about job submission

Following a broker decision jobs are to be submitted. Since all information about the selected computation resides within the 
selected ExecutionTarget, the ExecutionTarget is capable of returning a submitter (see next section) suitable submitting a 
job to the resource which is represents.}
\end{itemize}

@@

\chapter{Job Submission and Management}
\label{sec:JobManagement}
\section{Submission}
Almost every day a new grid cluster is purchased and made available around the world (either to the 
general public or restricted to authorized users). More available clusters create a need for better and 
faster resource discovery and information retrieval, making this task an utmost important component of the 
new client library.

\begin{itemize}
\item{{\bf Submitter} is base class}

\item{{\bf JobDescription} is }

\item{{\bf Broker} is }
\end{itemize}

\section{Management}
Almost every day a new grid cluster is purchased and made available around the world (either to the 
general public or restricted to authorized users). More available clusters create a need for better and 
faster resource discovery and information retrieval, making this task an utmost important component of the 
new client library.

\begin{itemize}
\item{{\bf JobSupervisor} is base class}

\item{{\bf JobController} is }

>>>>

Following a broker decision jobs are to be submitted. Since all information about the selected computation resides within the 
selected ExecutionTarget, the ExecutionTarget is capable of returning a submitter (see next section) capable of submitting a 
job to the resource which is represents.}
\end{itemize}

@@

\chapter{Job Submission and Management}
\label{sec:JobManagement}
\section{Submission}
Job submission starts with the resource discovery and target preparation as outlined in the section above. Not before a list 
of possible targets (which allows the user) is available is the job description read in order to enable bulk job submission of 
widely different jobs without having to reperform the resource discovery. The job submission makes use of the following classes:

\begin{itemize}
\item{{\bf Broker} is not yet implemented and thus not described here.}

\item{{\bf JobDescription} is responsible for handling all job descriptions. Thus it is capable of handling the xRSL, JDL and 
JSDL job description languages and to some extent also translate between them. Validation (syntax and semantical) is performed 
automatically when the source is set. Features easy retrieval of list of local input files which should be uploaded to the 
computing service.}

\item{{\bf Submitter} is base class for grid specific specializations (plugin).  It submits job(s) to a service and 
uploads (by the job needed) local input files. Returns an XML node containing all needed information about the job 
for later job management. The Submitter is returned by the ExecutionTarget selected for job execution and thus the 
ExecutionTarget populates (through XML config element) the Submitter with information about submission endpoint (URL) 
and job description languages ``spoken'' by the target.}

\end{itemize}

\begin{figure}[ht]
\centering{{\scalebox{0.75}{\includegraphics{JobSubmission.png}}}
\caption{\label{fig:JobSub}Diagram depicting the process of submitting a job to a computing service, including finding the 
best possible resource for the job.} }
\end{figure}

Figure \ref{fig:JobSub} shows a job submission sequence and below a description of each step is given:

\begin{enumerate}
\item{The TargetGenerator has prepared a list of targets. Depending on the URLs provided to the TargetGenerator the list of 
found targets may be empty or contain several targets. Targets may even represent more than one grid flavour. The list of 
found targets are taken as input to the Broker.}
\item{In order to choose between services the Broker needs to know the specific job requirements, thus the JobDescription is 
needed as input to the brokering process.}
\item{The broker outputs a ordered list of ExecutionTargets according to the provided JobDescription.}
\item{As explained in Section~\ref{sec:TargetDiscovery} each ExectionTarget has a method to return a specialized Submitter 
capable of submitting jobs to the service it represents. Thus the best suitable ExecutionTarget for the job is asked to return 
a Submitter for the submission.}
\item{The Submitter takes the JobDescription as input and uploads it to the computing service.}
\item{The Submitter identifies local input files from the JobDescription and uploads them to the computing service.}
\end{enumerate}

\section{Management}
Information about active jobs is stored in a local xml file which is used for later job management. As this file may contain 
information about jobs running on completely different grid flavours, job management should be handled using plugins similar to 
resource discovery and job submission. The following classes are used:

\begin{itemize}
\item{{\bf JobSupervisor} is responsible for loading the appropriate JobController for managing a job running on a specific 
grid flavour. In order to match a job identification string (jobid) with a grid flavour a lookup in the local xml file is 
performed. The JobSupervisor main functionality is to return a list of JobControllers which are capable of managing all jobs 
addressed by a certain command.}

\item{{\bf JobController} is both base class for grid specific specializations, but also the implementor of all public functionality 
offered by the JobControllers. In other words all virtual functions of the JobController are private. Upon initialization the 
JobController reads into and fills a local store of jobs called JobsStore.
The public functions of the 
JobController offer to get (download), clean, cancel, etc one or more jobs and uses the private specializations for issueing the command. 
This ensures consistency in how the commands are handled }
